Life in the canopy: Community trait assessments reveal substantial functional diversity among fern epiphytes

### 2020-02-07 ms/manuscript.Rmd
Use Roboto font

---
title: "Life in the canopy: Community trait assessments reveal substantial functional diversity among fern epiphytes"
bibliography: 
  - "references.bib"
  - "references_other.yaml"
fontsize: 12pt
output: 
  bookdown::pdf_document2:
    citation_package: none # Use pandoc default, otherwise csl can't be used for reference formatting
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: yes # need for converting tex to docx
    latex_engine: xelatex
    pandoc_args: [ "--csl", "new-phytologist.csl"]
    includes:
      in_header: new-phytologist.sty
header-includes: 
  - \usepackage{float}
  - \makeatletter\renewcommand*{\fps@figure}{H}\makeatother # Fix position of figs
  - \makeatletter\renewcommand*{\fps@table}{H}\makeatother # Fix position of tables
  - \usepackage{caption} # Needed to turn off automatic numbering of table captions
editor_options: 
  chunk_output_type: console
nocite: | 
  @Vogel1968
---

>>>>

---
title: "Life in the canopy: Community trait assessments reveal substantial functional diversity among fern epiphytes"
bibliography: 
  - "references.bib"
  - "references_other.yaml"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
- BoldFont=Roboto-Bold.ttf
- ItalicFont=Roboto-Italic.ttf
- BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: none # Use pandoc default, otherwise csl can't be used for reference formatting
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: yes # need for converting tex to docx
    latex_engine: xelatex
    pandoc_args: [ "--csl", "new-phytologist.csl"]
    includes:
      in_header: new-phytologist.sty
header-includes: 
  - \usepackage{float}
  - \makeatletter\renewcommand*{\fps@figure}{H}\makeatother # Fix position of figs
  - \makeatletter\renewcommand*{\fps@table}{H}\makeatother # Fix position of tables
  - \usepackage{caption} # Needed to turn off automatic numbering of table captions
editor_options: 
  chunk_output_type: console
nocite: | 
  @Vogel1968
---
